\documentclass[15pt]{article}
\usepackage{graphicx}
\graphicspath{{Images/}}

\usepackage{hyperref}
\hypersetup{colorlinks = true,citecolor = blue, linkcolor = blue, urlcolor = blue}

\setlength{\columnsep}{1.5cm}
\setlength{\columnseprule}{1pt}
 

\usepackage{fancyhdr}

\usepackage{biblatex}
\addbibresource{references.bib}

\lhead{Emerging Technologies in healthcare}
\rhead{CONTENTS}

\renewcommand{\headrulewidth}{0.5pt}
\rfoot{Page \thepage}
\fancyfoot[C,C]{Harshit Dhaduk}
\fancyfoot[L,L]{20-Feb-2022}
\renewcommand{\footrulewidth}{0.3pt} 


\begin{document}

\pagestyle{fancy}
\tableofcontents
\empty

\rule{\textwidth}{0.5pt}
\begin{abstract}
    The world is rapidly turning toward technological advancements 
    nd inventions. Science and technology have change dramatically 
    in the twenty-first century. We hear about a new idea or 
    innovation almost every day. The most fascinating aspect of this 
    relationship is that each new technology is a master of its 
    preceding incarnation.
    
    Artificial intelligence has simplified everything, whether it's 
    in shopping, education, or healthcare. Healthcare facilities have
    been gradually improving in recent years. Even at the time of the
    epidemic, COVID-19, healthcare had undergone significant changes 
    around the world. SCIENCE is the driving force behind this 
    endeavour.
\end{abstract}
\rule{\textwidth}{0.5pt}

\section{What is the importance of innovation and technology in healthcare?}
The advancement of technology not only modernises an individual's 
global position, but also makes our lives easier. Medical science has
enhanced world health more than ever before. Drugs and medicines are 
now available to everyone thanks to e-Pharmacy.

Scientists were able to better understand the human brain and its 
activities thanks to the concept of artificial intelligence. Long 
lines at hospital receptions have been replaced by online 
consultation options.

3D medicine printers have produced some effective life-saving 
medications. Nanomedicines, robotics, bioprinting, and other 
technologies have all contributed to the development of healthcare.

\section{What are the emerging technologies in healthcare?}

\subsection{3D bioprinting}
Bioprinting is a more advanced form of 3D printing. Bioprinting 
allows scientists to create tissues, bones, and blood arteries, among
other things. Even scientists believe that 3D bioprinting has allowed them to create an entire organ.
For medical students and trainees, this technology is a boon. This 
will assist to avoid the use of animals in clinical and 
pharmaceutical investigations in the future.

In addition, if scientists are successful in fully replicating the 
original human organ, it might be employed in transplant therapies. 
One of the branches of this application is Sprintam, which has been 
approved by the FDA.

\subsection{Nanomedicines}
This branch is concerned with the application of nanotechnology to 
medicine. Nanomedicines, also known as "future medicine," promise to
speed up drug delivery. These drugs are used to treat tumours and 
cancer in particular.

Nanomedicines are distinguished from conventional tools by their 
unique optical, magnetic, and radical properties. They are currently
used to detect the existence of cancers within the human body.

Nanomedicines encompasses not only pharmaceuticals but also the use 
of nanomaterials and biological devices in healthcare.

This application is now seeking ideas and breakthroughs from 
researchers all over the world. You can simply apply for your journal
if you have an idea that you believe will mark excellence in 
Nanomedicines.

\subsection{Cloud computing}
Cloud computing aids in the analysis and organisation of a patient's
information. It also promotes the patient's involvement in 
decision-making and empowers him to take charge of his own health.

Cloud computing has met the needs of the healthcare sector with 
features such as post-hospitalization plans, virtual medication, 
consultants, telemedicine, and more.

Cloud computing not only keeps a specific set of data safe, but it 
also aids in the organisation of worldwide data. Statistics and data
from the world's best hospitals are transmitted to a prominent 
research centre for analysis of health indices, common diseases, 
causative agents, and other factors.

\subsection{Digital health trackers}
The emergence of gadgets like step counts, blood pressure monitors, 
and respiratory rate monitors is a revolution in the healthcare 
industry. Even on a regular morning, we may witness a group of 
individuals jogging in the park while wearing the latest wristwatch 
and counting their steps.

Many such tracker apps are also accessible on Google Play and the 
Apple App Store. It raised public awareness about health and fitness
in the community. It also served as a first-aid treatment for modest
body rate abnormalities.

\subsection{e-Pharmacy}
Drugs and medicines are now available even in remote areas thanks to
the emergence of e-Pharmacy stores. PharmEasy and Netmeds, for 
example, are applications that not only assist in the discovery of 
vital pharmaceuticals but also provide a time-saving strategy.

If your loved one becomes unwell, you may decide whether you would 
want to spend your time wandering around looking for drugs for him 
or caring for him by downloading the prescription online.You’ll opt 
for the second option, right?

\subsection{Online consulting services}
Services such as Practo, Mfine, Tata Health, and others have made 
doctors available to patients at all hours of the day. This 
technique is beneficial to busy patients and those who do not want 
to queue for long periods of time. Tata Health, according to 
statistics, is the market leader in this area.

\subsection{Artificial intelligence}
In healthcare, artificial intelligence aids in the identification of
the human brain and the analysis of its algorithm.

For retinal analysis, a London hospital is employing artificial 
intelligence. It also aids scientists in the research of 
pre-clinical medication effects, allowing for more precise drug 
discovery and development. Artificial intelligence has been used in 
cardiology, neurology, and other fields of medicine.

\end{document}
